\documentclass[modern]{aastex631}

% Packages
\usepackage{microtype}  % ALWAYS!
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}

% Style tweaks
\renewcommand{\twocolumngrid}{\onecolumngrid}
\setlength{\parindent}{1.1\baselineskip}
\sloppy\sloppypar\raggedbottom\frenchspacing


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\shorttitle{Timing argument blah blah}
\shortauthors{Chamberlain, Price-Whelan et al.}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\graphicspath{{./}{figures/}}
\input{math_definitions.tex}

% Affiliations
\newcommand{\affuofa}{University of Arizona, 933 N. Cherry Ave,
    Tucson, AZ 85721, USA}
\newcommand{\affcca}{Center for Computational Astrophysics, Flatiron Institute,
    Simons Foundation, 162 Fifth Avenue, New York, NY 10010, USA}

\newcommand{\kc}[1]{\textcolor{mypink}{\textbf{#1}} }


%% This is the end of the preamble.  Indicate the beginning of the
%% manuscript itself with \begin{document}.

\begin{document} 

\title{
    A timing argument mass for the Local Group accounting for the
    Milky Way--LMC reflex motion
}

\author[0000-0001-8765-8670]{Katie~Chamberlain}
\affiliation{\affuofa}

\author[0000-0003-0872-7098]{Adrian~M.~Price-Whelan}
\affiliation{\affcca}

\author{Others!}


\begin{abstract}

    \textbf{Context} Timing argument, recently observed travel velocity after being predicted. \\
    \textbf{Aims} We introduce a Keplerian orbital model that accounts for the reflex motion of the Milky Way dist with respect to its outer halo to infer a Local Group mass using the Timing Argument.\\
    \textbf{Methods} We use Bayesian techniques to fit 
    the current 6D phase-space information of M31 and place constraints on the mass of the Local Group. \\
    \textbf{Results} We provide an updated Local Group mass of $4.69\pm0.71 \times 10^{12}$M$_\odot$ assuming a travel velocity of 32km/s, and find that the inferred mass depends strongly on the assumed travel velocity of the disk. \\
    \textbf{Conclusions}
    Introducing the Milky Way reflex motion yields lower Local Group mass estimates, which will be further constrained with updated travel velocity measurements. In addition, further improvements to the proper motion error from Gaia may improve the constraint on the Local Group mass by a factor of $\sim2$.


\end{abstract}

\section{Introduction}
\label{sec:intro}

\begin{itemize}
    \item importance of knowing mass of the local group
    \begin{itemize}
            \item 
            \item 
          \end{itemize}
    \item ways to measure local group mass
    \item \begin{itemize}
            \item other tracers? 
            \item introduction of timing argument 
            \item what previous TA measurements of the local group mass have been
          \end{itemize}
    \item what's wrong with previous use of TA?
        \begin{itemize}
            \item the LMC is massive and pulling on the MW disk
            \item previous use of timing argument did not account for travel velocity of the disk
            \item we include the travel velocity of the disk
        \end{itemize}
    \item cosmological impact
        \begin{itemize}
            \item bias and calibration of the timing argument 
            \item what a lower/higher group mass means (we're gonna be more consistent w other group mass measurements, I think?)
        \end{itemize}
    
\end{itemize}


\section{The timing argument as a Local Group mass estimator}
\label{sec:timing}


\section{Data analysis and methods}
\label{sec:methods}


\section{Results: Local group mass estimates}
\label{sec:results}


\section{Comparison to M33--M31 system}
\label{sec:results}


\section{Summary and Discussion}
\label{sec:discussion}


\software{
    Astropy \citep{astropy, astropy:2018},
    gala \citep{gala},
    IPython \citep{ipython},
    numpy \citep{numpy},
    % pymc3 \citep{Salvatier2016},
    scipy \citep{scipy}
}

\appendix
For baddies only.

\bibliography{refs}{}
\bibliographystyle{aasjournal}

\end{document}
